---
title: "Atelier 4"
author: "Marion VICHARD"
date: "13/11/2019"
output:
  word_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Option 1 (taille)

```{r}
nutriage <- read.csv("~/Desktop/Atelier4-master/nutriage.csv")
names(nutriage)
```
```{r}
hist(nutriage$taille)
summary(nutriage$taille)
```

Hypothèse : taille $\sim N(\mu,\sigma)$ le problème est $\Pr(taille < 0) >0$

```{r}
mean(nutriage$taille) 
sd(nutriage$taille)
```

On va calculer $\Pr(taille < 0)$ avec $taille \sim N(163.9602, 9.003368)$

```{r}
pnorm(0,mean(nutriage$taille),sd(nutriage$taille))
```

## Option 2 (taille)

Soit $taille=e^X$ avec $X \sim N(mu, \sigma).$ Alors $X = ln(taille).$

```{r}
X <- log(nutriage$taille)
hist(X)
summary(X)
Q <- seq(from=0, to=1, by=0.1)
Q
qnorm(Q)

```

qq plot 

```{r}
Z <- (X-mean(X))/sd(X)
n <- length(Z) 
n 
Normal <- rnorm(n)
qqplot(Normal,Z,xlim=c(-3,3), ylim=c(-3,3))
par (new=T)
plot(Z,Z,type="l",col="red",xlim=c(-3,3),ylim=c(-3,3),xlabel="",ylabel="")
```



## Option 1 (poids)

```{r}
nutriage <- read.csv("~/Desktop/Atelier4-master/nutriage.csv")
names(nutriage)
```

```{r}
hist(nutriage$poids)
summary(nutriage$poids)
```

Hypothèse : poids $\sim N(\mu,\sigma)$ le problème est $\Pr(poids < 0) >0$

```{r}
mean(nutriage$poids) 
sd(nutriage$poids)
```

On va calculer $\Pr(poids < 0)$ avec $poids \sim N(163.9602, 9.003368)$

```{r}
pnorm(0,mean(nutriage$poids),sd(nutriage$poids))
```

## Option 2 (poids)

Soit $poids=e^X$ avec $X \sim N(mu, \sigma).$ Alors $X = ln(poids).$

```{r}
X <- log(nutriage$poids)
hist(X)
summary(X)
Q <- seq(from=0, to=1, by=0.1)
Q
qnorm(Q)

```

qq plot 

```{r}
Z <- (X-mean(X))/sd(X)
n <- length(Z) 
n 
Normal <- rnorm(n)
qqplot(Normal,Z,xlim=c(-3,3),ylim=c(-3,3),xlab="Normal",ylab="log(poids)")
par (new=T)
plot(Z,Z,type="l",col="red",xlim=c(-3,3),ylim=c(-3,3),xlab="",ylab="")
```

Cafe 

```{r}
table(nutriage$cafe)
mean(nutriage$cafe)
var(nutriage$cafe)
lambda <- (mean(nutriage$cafe)+var(nutriage$cafe))/2
lambda 
simul <- rpois(1000,lambda)
table(simul)
```

Thé 

```{r}
table(nutriage$the)
mean(nutriage$the)
var(nutriage$the)
lambda <- (mean(nutriage$the)+var(nutriage$the))/2
lambda 
simul <- rpois(1000,lambda)
table(simul)
```






























